### 2022-11-20 ms.rmd
orchard

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp)

@@

# Intercept only model. 
model1.1 <- metafor::rma.mv(effect_size ~ type, V = V, 
                            random = list(~1 + type | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | obs),
                            R = list(species_full = phylo_cor), dfs = "contain", test = "t", data = lnRRQ10_data)

>>>>

##################################
# Loading packages & Functions
##################################
    pacman::p_load(tidyverse,  metafor, flextable, raster, rasterVis,  patchwork, RColorBrewer, ggtree, ape, phytools, viridis, MCMCglmm, brms, latex2exp, orchaRd)

@@

# Intercept only model. 
model1.1 <- metafor::rma.mv(effect_size ~ type, V = V, 
                            random = list(~1 + type | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | obs),
                            R = list(species_full = phylo_cor), dfs = "contain", test = "t", data = lnRRQ10_data)
model1.1_rob <- robust(model1.1, cluster = lnRRQ10_data$record_num)
orchaRd::orchard_plot(model1.1, mod = "type", group  = "record_num", data = lnRRQ10_data, xlab = "lnRRQ10")
